Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-08 doc/Paper/main.tex
More figure updates and changed numbers given in text.

    \begin{table*}
      \caption{\todo{UPDATE} Summary of parameters varied in the MCMC with their respective priors. The posterior means and best-fits denote the values derived for our fiducial analysis. The uncertainties denote the $68 \%$ c.l..} \label{tab:params}
      \begin{center}
        \begin{tabular}{cccc}
          \hline\hline 
          Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $12.29 \pm 0.15$ & $12.25$ \\ 
          $M_{\mathrm{min}, p}$ & flat $\in [-5., \,10.]$ & $2.93\substack{+1.56 \\ -1.47}$ & $1.83$ \\
          $M_{0}$ & flat $\in [0., \,15.]$ & $5.97 \pm 4.00$ & $8.36$ \\
          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.65 \pm 5.00$ & $7.58$ \\
          $M_{1}$ & flat $\in [0., \,15.]$ & $13.69 \pm 0.21$ & $13.63$ \\ 
          $M_{1, p}$ & flat $\in [-5., \,15.]$ & $6.00\substack{+2.14 \\ -2.05}$ & $4.49$ \\
          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.0170\substack{+0.091 \\ -0.090}$ & $-0.0525$ \\
          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $0.00470\substack{+0.095 \\ -0.093}$ & $-0.0321$ \\
          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $0.0198\substack{+0.101 \\ -0.099}$ & $0.0136$ \\
          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0337\substack{+0.106 \\ -0.105}$ & $0.0174$ \\
          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0361\substack{+0.1376 \\ -0.1234}$ & $-0.159$ \\
          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.0252 \pm 0.0799$ & $-0.00141$ \\
          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0569\substack{+0.0856 \\ -0.0897}$ & $0.0576$ \\
          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0153\substack{+0.1190 \\ -0.1217}$ & $0.0467$ \\ \\
          $A_{\mu}$ & flat $\in [-2., \,2.]$ & $ - $ & $ - $ \\
          $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
          $\sigma_{8}$ & flat $\in [0.4, \,1.5]$ & $ - $ & $ - $ \\
          \hline\hline 
        \end{tabular}
      \end{center}
    \end{table*}

@@

Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}. The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}. As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}. Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra. The corresponding minimum $\chi^{2}$ is $\chi^{2} = 95.8$. Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.20$ ($p$-value $= 0.11$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g. \cite{Andrae:2010}). However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.

In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}$ and the mass scale for satellites $M_{1}$ obtained in our analysis. To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs. As can be seen, we find that the data prefer both a decreasing $M_{\mathrm{min}}$ and $M_{1}$. This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift since galaxies will only form in the most massive halos at early times. We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}.

@@

\begin{sidewaystable}
\caption{\todo{UPDATE last 4 entries} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
\begin{center}
\begin{tabular}{ccccccccc}
\hline\hline 
Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
auto & $\sfrac{18.0}{25}$ $(0.84)$ & $-0.665\substack{2.66 \\ -2.72}$ & $11.78\substack{0.31 \\ -0.28}$ & $0.705\substack{+3.29 \\ -3.30}$ & $12.95\substack{+0.37 \\ -0.33}$  & - & - & - \\
G cov & $\sfrac{84.0}{80}$ $(0.36)$ & $0.361\substack{+3.06 \\ -2.63}$ & $11.89\substack{+0.23 \\ -0.24}$ & $2.01\substack{+3.97 \\ -3.41}$ & $13.09\substack{+0.28 \\ -0.29}$ & - & - & - \\
G+SSC cov & $\sfrac{83.0}{80}$ $(0.39)$ & $-0.370\substack{+2.38 \\ -2.18}$ & $11.87\substack{+0.24 \\ -0.25}$ & $1.12\substack{+3.05 \\ -2.75}$ & $13.06\substack{+0.29 \\ -0.30}$ & - & - & - \\
no $z_{w, i}$ & $\sfrac{83.6}{84}$ $(0.49)$ & $0.770\substack{+0.679 \\ -0.891}$ & $11.86\substack{+0.13 \\ -0.14}$ & $0.494\substack{+0.929 \\ -1.21}$ & $13.05\substack{+0.18 \\ -0.20}$ & - & - & - \\
no $z_{w, i}, \Delta z_{i}$ & $\sfrac{90.2}{88}$ $(0.42)$ & $-1.16\substack{+0.632 \\ -0.845}$ & $11.75 \pm 0.14$ & $-0.130\substack{+0.687 \\ -1.01}$ & $12.89 \pm 0.17$ & - & - & - \\
bins = 0, 1, 2 & $\sfrac{41.0}{43}$ $(0.56)$ & $-0.408\substack{+2.35 \\ -2.46}$ & $11.84 \pm 0.25$ & $0.585\substack{+2.84 \\ -2.99}$ & $13.03\substack{+0.31 \\ -0.30}$ & - & - & - \\
bins = 1, 2, 3 & $\sfrac{42.6}{46}$ $(0.62)$ & $1.22\substack{+3.27 \\ -3.22}$ & $11.94\substack{+0.34 \\ -0.39}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
pz = \texttt{Ephor\_AB} & $\sfrac{89.6}{80}$ $(0.22)$ & $0.396\substack{+2.2 \\ -2.1}$ & $12.12\substack{+0.20 \\ -0.19}$ & $2.02\substack{+3.07 \\ -2.88}$ & $13.37\substack{+0.27 \\ -0.26}$ & - & - & - \\
pz = \texttt{Ephor} & $\sfrac{102.0}{80}$ $(0.049)$ & $1.16\substack{+2.02 \\ -2.09}$ & $12.14\substack{+0.18 \\ -0.17}$ & $3.01\substack{+2.75 \\ -2.87}$ & $13.39\substack{+0.23 \\ -0.22}$ & - & - & - \\
pz = \texttt{DEmP} & $\sfrac{100.8}{80}$ $(0.058)$ & $0.493\substack{+1.93 \\ -1.97}$ & $12.03 \pm 0.20$ & $2.15\substack{+2.64 \\ -2.67}$ & $13.25 \pm 0.27$ & - & - & - \\
pz = \texttt{FRANKEN-Z} & $\sfrac{87.2}{80}$ $(0.27)$ & $0.387\substack{+1.99 \\ -1.96}$ & $12.13 \pm 0.18$ & $2.00\substack{+2.79 \\ -2.74}$ & $13.38 \pm 0.24$ & - & - & - \\
fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
 \hline \hline
\end{tabular}
\end{center}
\end{sidewaystable}

As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross power spectra. However, cross correlations between redshift bins are susceptible to photometric redshift errors, such as outliers. In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross power spectra. Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone. As can be seen, the constraints from auto power spectra and auto- and cross power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis. Furthermore, we see that the constraining power on HOD parameters is unaffected by including the cross power spectra. As a final consistency check between auto- and cross power spectra we test how well the auto power spectra predict the cross power spectra. To this end we compute the $\chi^{2}$ between the observed auto- and cross power spectra and the theoretical predictions derived from auto power spectra only. As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test. We find $\chi^{2} = 102.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra (see Tab.~\ref{tab:constraints_robustness}). This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.

An important part of our data model is the analytical covariance matrix described in Sec.~\ref{sssec:methods.theory.covar}. In order to test the impact of the non-Gaussianity of the covariance on our results, we compare the HOD constraints obtained accounting for Gaussian (G) and Gaussian and SSC contributions (G+SSC) to our fiducial constraints, which include Gaussian, SSC and non-Gaussian contributions. As can be seen from Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}, these constraints agree very well with each other. The constraints from the G and the G+SSC case yield almost identical constraints, which is expected due to the suppression of the SSC contribution by the number density correction (c.f. Sec.~\ref{ssec:results.covariance}). Accounting for all non-Gaussian contributions to the covariance results in slightly broadened but consistent constraints. Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales and therefore do not have a significant impact when computing constraints from all power spectra. Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data increase as we account for less contributions to the total covariance, as expected. However, we find an acceptable goodness of fit, even when only accounting for the Gaussian covariance.

@@

In Fig.~\ref{fig:constraints-pz-syst-auto+cross-vs-auto}, we show the constraints on photometric redshift systematics parameters derived in our fiducial analysis. We find that the data cannot separately constrain the mean shift parameters $\Delta z_{i}$, as opposed to pairwise differences between those. We therefore show the constraints in terms of the reparametrized parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively. While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.021$ ($68 \%$ c.l.). This means that the data do not allow constraining the absolute position of each redshift bin, but are quite sensitive to their relative positions.

@@

The discrepancies between HOD parameters derived from the five different methods become even stronger when we do not account for photo-$z$ uncertainties, as can be seen from Fig.~\ref{fig:constraints-HOD-no-pz-shifts-pz-methods}. In contrast to the results obtained using our fiducial COSMOS30 photo-$z$ distributions, we find that we cannot obtain an acceptable fit to the data for the alternative four methods when not accounting for photometric redshift uncertainties. The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 2.08$ and $\chi^{2}_{\mathrm{red}} = 5.04$. This suggests that the data are able to detect the presence of significant photometric redshift errors in the distributions derived using the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to those derived using COSMOS 30-band data.

@@

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}} 
\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}} 
\caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model. The third panel illustrates the empirical scaling $b(z) \sim \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
\label{fig:HOD-redshift}
\end{center}
\end{figure}

>>>>

    \begin{table*}
      \caption{Summary of parameters varied in the MCMC with their respective priors. The posterior means and best-fits denote the values derived for our fiducial analysis. The uncertainties denote the $68 \%$ c.l..} \label{tab:params}
      \begin{center}
        \begin{tabular}{cccc}
          \hline\hline 
          Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $11.89\substack{+0.24 \\ -0.25}$ & $11.76$ \\ 
          $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $-2.95$ \\
          $M_{0}$ & flat $\in [0., \,15.]$ & $5.85\substack{+4.03 \\ -4.05}$ & $5.58$ \\
          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.33\substack{+5.12 \\ -4.93}$ & $-0.925$ \\
          $M_{1}$ & flat $\in [0., \,15.]$ & $13.09\substack{+0.24 \\ -0.25}$ & $12.96$ \\ 
          $M_{1, p}$ & flat $\in [-10., \,15.]$ & $1.49\substack{+3.21 \\ -3.08}$ & $-2.07$ \\
          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000147\substack{+0.102 \\ -0.096}$ & $-0.0456$ \\
          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0128\substack{+0.103 \\ -0.096}$ & $-0.0923$ \\
          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00170\substack{+0.109 \\ -0.104}$ & $-0.103$ \\
          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0148\substack{+0.109 \\ -0.106}$ & $-0.0727$ \\
          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0300\substack{+0.130 \\ -0.119}$ & $-0.177$ \\
          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.000837\substack{+0.0780 \\ -0.0785}$ & $-0.0991$ \\
          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0342\substack{+0.0825 \\ -0.0794}$ & $0.0243$ \\
          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0355\substack{+0.122 \\ -0.138}$ & $0.151$ \\ \\
          $A_{\mu}$ & flat $\in [-3., \,3.]$ & $ - $ & $ - $ \\
          $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
          $\sigma_{8}$ & flat $\in [0.4, \,1.5]$ & $ - $ & $ - $ \\
          \hline\hline 
        \end{tabular}
      \end{center}
    \end{table*}

@@

Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}. The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}. As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}. Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra. The corresponding minimum $\chi^{2}$ is $\chi^{2} = 82.0$. Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.03$ ($p$-value $= 0.42$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g. \cite{Andrae:2010}). However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.

In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}$ and the mass scale for satellites $M_{1}$ obtained in our analysis. To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs. As can be seen, we find that, within or uncertainties, the data prefer both a constant $M_{\mathrm{min}}$ and $M_{1}$. This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift since galaxies will only form in the most massive halos at early times. We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}.

@@

\begin{sidewaystable}
\caption{\todo{UPDATE last 4 entries} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
\begin{center}
\begin{tabular}{ccccccccc}
\hline\hline 
Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
auto & $\sfrac{18.0}{25}$ $(0.84)$ & $-0.665\substack{2.66 \\ -2.72}$ & $11.78\substack{0.31 \\ -0.28}$ & $0.705\substack{+3.29 \\ -3.30}$ & $12.95\substack{+0.37 \\ -0.33}$  & - & - & - \\
G cov & $\sfrac{83.4}{80}$ $(0.38)$ & $-0.0602\substack{+2.71 \\ -2.16}$ & $11.91\substack{+0.20 \\ -0.21}$ & $1.46\substack{+3.36 \\ -2.78}$ & $13.10\substack{+0.25 \\ -0.26}$ & - & - & - \\
G+SSC cov & $\sfrac{83.0}{80}$ $(0.39)$ & $-0.370\substack{+2.38 \\ -2.18}$ & $11.87\substack{+0.24 \\ -0.25}$ & $1.12\substack{+3.05 \\ -2.75}$ & $13.06\substack{+0.29 \\ -0.30}$ & - & - & - \\
no $z_{w, i}$ & $\sfrac{83.6}{84}$ $(0.49)$ & $0.770\substack{+0.679 \\ -0.891}$ & $11.86\substack{+0.13 \\ -0.14}$ & $0.494\substack{+0.929 \\ -1.21}$ & $13.05\substack{+0.18 \\ -0.20}$ & - & - & - \\
no $z_{w, i}, \Delta z_{i}$ & $\sfrac{90.2}{88}$ $(0.42)$ & $-1.16\substack{+0.632 \\ -0.845}$ & $11.75 \pm 0.14$ & $-0.130\substack{+0.687 \\ -1.01}$ & $12.89 \pm 0.17$ & - & - & - \\
bins = 0, 1, 2 & $\sfrac{41.0}{43}$ $(0.56)$ & $-0.408\substack{+2.35 \\ -2.46}$ & $11.84 \pm 0.25$ & $0.585\substack{+2.84 \\ -2.99}$ & $13.03\substack{+0.31 \\ -0.30}$ & - & - & - \\
bins = 1, 2, 3 & $\sfrac{42.6}{46}$ $(0.62)$ & $1.22\substack{+3.27 \\ -3.22}$ & $11.94\substack{+0.34 \\ -0.39}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
pz = \texttt{Ephor\_AB} & $\sfrac{89.6}{80}$ $(0.22)$ & $0.396\substack{+2.2 \\ -2.1}$ & $12.12\substack{+0.20 \\ -0.19}$ & $2.02\substack{+3.07 \\ -2.88}$ & $13.37\substack{+0.27 \\ -0.26}$ & - & - & - \\
pz = \texttt{Ephor} & $\sfrac{102.0}{80}$ $(0.049)$ & $1.16\substack{+2.02 \\ -2.09}$ & $12.14\substack{+0.18 \\ -0.17}$ & $3.01\substack{+2.75 \\ -2.87}$ & $13.39\substack{+0.23 \\ -0.22}$ & - & - & - \\
pz = \texttt{DEmP} & $\sfrac{100.8}{80}$ $(0.058)$ & $0.493\substack{+1.93 \\ -1.97}$ & $12.03 \pm 0.20$ & $2.15\substack{+2.64 \\ -2.67}$ & $13.25 \pm 0.27$ & - & - & - \\
pz = \texttt{FRANKEN-Z} & $\sfrac{87.2}{80}$ $(0.27)$ & $0.387\substack{+1.99 \\ -1.96}$ & $12.13 \pm 0.18$ & $2.00\substack{+2.79 \\ -2.74}$ & $13.38 \pm 0.24$ & - & - & - \\
fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
 \hline \hline
\end{tabular}
\end{center}
\end{sidewaystable}

As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross power spectra. However, cross correlations between redshift bins are susceptible to photometric redshift errors, such as outliers. In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross power spectra. Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone. As can be seen, the constraints from auto power spectra and auto- and cross power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis. Furthermore, we see that the constraining power on HOD parameters is unaffected by including the cross power spectra. As a final consistency check between auto- and cross power spectra we test how well the auto power spectra predict the cross power spectra. To this end we compute the $\chi^{2}$ between the observed auto- and cross power spectra and the theoretical predictions derived from auto power spectra only. As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test. We find $\chi^{2} = 90.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}). This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.

An important part of our data model is the analytical covariance matrix described in Sec.~\ref{sssec:methods.theory.covar}. In order to test the impact of the non-Gaussianity of the covariance on our results, we compare the HOD constraints obtained accounting for Gaussian (G) and Gaussian and SSC contributions (G+SSC) to our fiducial constraints, which include Gaussian, SSC and non-Gaussian contributions. As can be seen from Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}, these constraints agree very well with each other. The constraints from the G and the G+SSC case yield almost identical constraints, which is expected due to the suppression of the SSC contribution by the number density correction (c.f. Sec.~\ref{ssec:results.covariance}). Accounting for all non-Gaussian contributions to the covariance results in slightly broadened but consistent constraints. Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales and therefore do not have a significant impact when computing constraints from all power spectra. Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data slightly increase as we account for less contributions to the total covariance, as expected. However, we find an acceptable goodness of fit, even when only accounting for the Gaussian covariance.

@@

In Fig.~\ref{fig:constraints-pz-syst-auto+cross-vs-auto}, we show the constraints on photometric redshift systematics parameters derived in our fiducial analysis. We find that the data cannot separately constrain the mean shift parameters $\Delta z_{i}$, as opposed to pairwise differences between those. We therefore show the constraints in terms of the reparametrized parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively. While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.). This means that the data do not allow constraining the absolute position of each redshift bin, but are quite sensitive to their relative positions.

@@

The discrepancies between HOD parameters derived from the five different methods become even stronger when we do not account for photo-$z$ uncertainties, as can be seen from Fig.~\ref{fig:constraints-HOD-no-pz-shifts-pz-methods}. In contrast to the results obtained using our fiducial COSMOS30 photo-$z$ distributions, we find that we cannot obtain an acceptable fit to the data for the alternative four methods when not accounting for photometric redshift uncertainties. The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 1.88$ and $\chi^{2}_{\mathrm{red}} = 4.88$. This suggests that the data are able to detect the presence of significant photometric redshift errors in the distributions derived using the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to those derived using COSMOS 30-band data.

@@

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.32\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}} 
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}} 
\caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model. The third panel illustrates the empirical scaling $b(z) \sim \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
\label{fig:HOD-redshift}
\end{center}
\end{figure}
